Relative Stable Maps in Genus One via Central Alignments

### 2018-03-22 genus-one-relative-maps.tex
didn't change anything

We have thus shown that when we restrict $\Lcal$ to either an external component or an internal component (where here we mean a connected component of $f^{-1}(Y)$) we get the correct line bundle. Assuming that there is no wheel of $\PP^1$s, or more generally that any wheel of $\PP^1$s which does appear appears inside a connected component, this shows that $\Lcal_{\Ccal_0} = L$, as claimed.

>>>>

We have thus shown that when we restrict $\Lcal$ to either an external component or an internal component (where here we mean a connected component of $f^{-1}(Y)$) we get the correct line bundle. Assuming that there is no wheel of $\PP^1$s, or more generally that any wheel of $\PP^1$s which does appear appears inside a connected component, this shows that $\Lcal_{\Ccal_0} = L$, as claimed.\basenote{What about in general?}
